Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-17 paper/arxiv/supp_4_others.tex
fix table note format

% Supplementary Table 19: Packages in the DL env
\begin{table}[htbp]
\label{supp_table19:pack_dl_env}
  \caption{Core packages in the deep learning environment}
  \small
  \begin{tabularx}{\textwidth}{@{}l *{3}{X} @{}}
    \toprule
    Name                 & Version  & Build                         & Channel      \\
    \midrule
    conda                & 4.13.0   & py39h06a4308\textunderscore0  & anaconda     \\
    cuda-nvcc            & 11.8.89  & 0                             & nvidia       \\
    cuda-toolkit         & 11.8.0   & 0                             & nvidia       \\
    cudatoolkit          & 11.6.0   & habf752d\textunderscore9      & nvidia       \\
    ipykernel            & 6.9.1    & py39h06a4308\textunderscore0  & anaconda     \\
    ipython              & 7.34.0   & pypi\textunderscore0          & pypi         \\
    jupyter\_client      & 7.2.2    & py39h06a4308\textunderscore0  & anaconda     \\
    jupyterlab           & 3.4.4    & py39h06a4308\textunderscore0  & anaconda     \\
    keras                & 2.9.0    & pypi\textunderscore0          & pypi         \\
    keras-preprocessing  & 1.1.2    & pypi\textunderscore0          & pypi         \\
    keras-tuner          & 1.3.5    &                               & pypi         \\
    matplotlib           & 3.5.1    & py39h06a4308\textunderscore1  & anaconda     \\
    numpy                & 1.22.4   & pypi\textunderscore0          & pypi         \\
    pandas               & 1.3.4    & py39h8c16a72\textunderscore0  & anaconda     \\
    python               & 3.9.12   & h12debd9\textunderscore1      & anaconda     \\
    scikit-learn         & 1.1.1    & py39h6a678d5\textunderscore0  & anaconda     \\
    scipy                & 1.8.1    & py39hddc5342\textunderscore3  & conda-forge  \\
    tensorboard          & 2.9.1    & pypi\textunderscore0          & pypi         \\
    tensorflow           & 2.9.3    & pypi\textunderscore0          & pypi         \\
    tensorflow-gpu       & 2.9.3    & pypi\textunderscore0          & pypi         \\
    xlrd                 & 2.0.1    & pyhd3eb1b0\textunderscore0    & anaconda     \\
    yaml                 & 0.2.5    & h7b6447c\textunderscore0      & anaconda     \\
    \bottomrule
  \end{tabularx}
  \bigskip
  \small\textit{Note:} The complete list of packages is
    provided along with the source code
\end{table}

@@

% Supplementary Table 20: Packages in data analysis and vis env
\begin{table}[htbp]
\label{supp_table20:pack_vis_env}
  \caption{Core packages in data analysis and visualization environment}
  \small
  \begin{tabularx}{\textwidth}{@{}l *{3}{X} @{}}
    \toprule
    Name              & Version  & Build                     & Channel  \\
    \midrule
    bokeh             & 3.2.2    & pypi\textunderscore0      & pypi     \\
    colorcet          & 3.0.1    & pypi\textunderscore0      & pypi     \\
    heatmapz          & 0.0.4    & pypi\textunderscore0      & pypi     \\
    keras             & 2.13.1   & pypi\textunderscore0      & pypi     \\
    keras-tuner       & 1.3.5    & pypi\textunderscore0      & pypi     \\
    matplotlib        & 3.7.2    & pypi\textunderscore0      & pypi     \\
    numpy             & 1.24.3   & pypi\textunderscore0      & pypi     \\
    pandas            & 2.0.3    & pypi\textunderscore0      & pypi     \\
    python            & 3.11.4   & hb885b13\textunderscore0  &          \\
    pyyaml            & 6.0.1    & pypi\textunderscore0      & pypi     \\
    scikit-learn      & 1.3.0    & pypi\textunderscore0      & pypi     \\
    scipy             & 1.11.1   & pypi\textunderscore0      & pypi     \\
    seaborn           & 0.12.2   & pypi\textunderscore0      & pypi     \\
    tensorboard       & 2.13.0   & pypi\textunderscore0      & pypi     \\
    tensorflow        & 2.13.0   & pypi\textunderscore0      & pypi     \\
    tensorflow-macos  & 2.13.0   & pypi\textunderscore0      & pypi     \\
    \bottomrule
  \end{tabularx}
  \bigskip
  \small\textit{Note:} The complete list of packages
    is provided along with the source code.
\end{table}

>>>>

% Supplementary Table 19: Packages in the DL env
\begin{table}[htbp]
\label{supp_table19:pack_dl_env}
  \caption{Core packages in the deep learning environment}
  \small
  \begin{tabularx}{\textwidth}{@{}l *{3}{X} @{}}
    \toprule
    Name                 & Version  & Build                         & Channel      \\
    \midrule
    conda                & 4.13.0   & py39h06a4308\textunderscore0  & anaconda     \\
    cuda-nvcc            & 11.8.89  & 0                             & nvidia       \\
    cuda-toolkit         & 11.8.0   & 0                             & nvidia       \\
    cudatoolkit          & 11.6.0   & habf752d\textunderscore9      & nvidia       \\
    ipykernel            & 6.9.1    & py39h06a4308\textunderscore0  & anaconda     \\
    ipython              & 7.34.0   & pypi\textunderscore0          & pypi         \\
    jupyter\_client      & 7.2.2    & py39h06a4308\textunderscore0  & anaconda     \\
    jupyterlab           & 3.4.4    & py39h06a4308\textunderscore0  & anaconda     \\
    keras                & 2.9.0    & pypi\textunderscore0          & pypi         \\
    keras-preprocessing  & 1.1.2    & pypi\textunderscore0          & pypi         \\
    keras-tuner          & 1.3.5    &                               & pypi         \\
    matplotlib           & 3.5.1    & py39h06a4308\textunderscore1  & anaconda     \\
    numpy                & 1.22.4   & pypi\textunderscore0          & pypi         \\
    pandas               & 1.3.4    & py39h8c16a72\textunderscore0  & anaconda     \\
    python               & 3.9.12   & h12debd9\textunderscore1      & anaconda     \\
    scikit-learn         & 1.1.1    & py39h6a678d5\textunderscore0  & anaconda     \\
    scipy                & 1.8.1    & py39hddc5342\textunderscore3  & conda-forge  \\
    tensorboard          & 2.9.1    & pypi\textunderscore0          & pypi         \\
    tensorflow           & 2.9.3    & pypi\textunderscore0          & pypi         \\
    tensorflow-gpu       & 2.9.3    & pypi\textunderscore0          & pypi         \\
    xlrd                 & 2.0.1    & pyhd3eb1b0\textunderscore0    & anaconda     \\
    yaml                 & 0.2.5    & h7b6447c\textunderscore0      & anaconda     \\
    \bottomrule
  \end{tabularx}

  \smallskip

  \footnotesize\textit{Note:} The complete list of packages is
    provided along with the source code
\end{table}

@@

% Supplementary Table 20: Packages in data analysis and vis env
\begin{table}[htbp]
\label{supp_table20:pack_vis_env}
  \caption{Core packages in data analysis and visualization environment}
  \small
  \begin{tabularx}{\textwidth}{@{}l *{3}{X} @{}}
    \toprule
    Name              & Version  & Build                     & Channel  \\
    \midrule
    bokeh             & 3.2.2    & pypi\textunderscore0      & pypi     \\
    colorcet          & 3.0.1    & pypi\textunderscore0      & pypi     \\
    heatmapz          & 0.0.4    & pypi\textunderscore0      & pypi     \\
    keras             & 2.13.1   & pypi\textunderscore0      & pypi     \\
    keras-tuner       & 1.3.5    & pypi\textunderscore0      & pypi     \\
    matplotlib        & 3.7.2    & pypi\textunderscore0      & pypi     \\
    numpy             & 1.24.3   & pypi\textunderscore0      & pypi     \\
    pandas            & 2.0.3    & pypi\textunderscore0      & pypi     \\
    python            & 3.11.4   & hb885b13\textunderscore0  &          \\
    pyyaml            & 6.0.1    & pypi\textunderscore0      & pypi     \\
    scikit-learn      & 1.3.0    & pypi\textunderscore0      & pypi     \\
    scipy             & 1.11.1   & pypi\textunderscore0      & pypi     \\
    seaborn           & 0.12.2   & pypi\textunderscore0      & pypi     \\
    tensorboard       & 2.13.0   & pypi\textunderscore0      & pypi     \\
    tensorflow        & 2.13.0   & pypi\textunderscore0      & pypi     \\
    tensorflow-macos  & 2.13.0   & pypi\textunderscore0      & pypi     \\
    \bottomrule
  \end{tabularx}

  \smallskip

  \footnotesize\textit{Note:} The complete list of packages
    is provided along with the source code.
\end{table}
